Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-06-10 thesis/chapters/ch_chapter4.tex
Bugfix with extra sub in subsection

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.}
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

\subsubsection{Variation with SFR}
\label{ch4:sec:SFR}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines; CNM: dark blue, WNM: light blue, WIM: orange, HIM: red), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases sum to the black, dashed line. }
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

\subsection{Variation with SFR}
\label{ch4:sec:SFR}
